Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-09-17 latex/robdml.tex
u

Despite the improvements of this field thanks to the advancement of deep neural
networks, recent research works suggest that DML models are vulnerable to
adversarial attacks, where an imperceptible perturbation could incur unexpected
or covertly manipulated results~[].
%
Such vulnerability poses safety, security, and fairness concerns in the
applications of DML.
%
For example, impersonation or recognition evation are possible for DML-based
face-identification system~[].
%
Thus, defending a DML model against adversarial attacks and improving its
adversarial robustness could be an important problem.

% existing methods & problem
existing methods and problem.

% for problem 1
solution to problem 1

% for problem 2
solution to problem 2

@@

% contributions
In brief, our contribusions include:

>>>>

Despite the improvements of this field thanks to the advancement of deep neural
networks, recent research works suggest that DML models are vulnerable to
adversarial attacks, where an imperceptible perturbation could incur unexpected
or covertly manipulated results~[].
%
Such vulnerability poses safety, security, and fairness concerns in the
applications of DML.
%
For example, impersonation or recognition evation are possible for DML-based
face-identification system~[].
%
To counter the attacks (or reducing the vulnerability), it is important to
design defense methods to improve the adversarial robustness of DML models.

% existing methods & problem
A series of defense methods for DML are proposed~[], inspired by the Madry's
adversarial training method~[], as it is kown as one of the most effective
defense methods for deep neural network classifiers.
%
However, it has been noted that
%
(1) the direct adoptation of Madry's defense will easily lead to model collapse
due to producing very hard sample triplets;
%
(2) \oo{the sota defense lacks ()};
%
and (3) the adversarial training procedure is very time-consuming compared
to the training process of a regular DML model.

% for problem 1
Triplet hardness still matters in adversarial training for deep metric
learning.
%
propose hardness manipulation for.
solution to problem 1

% for problem 2
ACT and amdsemi have distinct characteristics.
solution to problem 2

% for problem 3
update of advtrain acceleration.
solution to problem 3

@@

% contributions
In brief, our contribusions include:
%
\begin{enumerate}
	%
	\item Hardness manipulation and the finding. better robustness.
		%
	\item Combine and even better.
		%
	\item Accelerate and reduce the cost for reproducing and applying.
		%
\end{enumerate}
